Stack Safety as a Security Property

### 2020-07-07 main.tex
Wondering how to phrase the various policies

\leo{Policies of interest: null, micro, cherri, software-only}
\leo{TODO: Write down carefully}

>>>>

This model is flexible enough to capture any kind of mechanism used for dynamic
enforcement of properties of interest, including the following representative
families of policies.

%% \leo{Policies of interest: null, micro, cherri, software-only}
%% \leo{TODO: Write down carefully}

\paragraph*{Null policy}
%
The simplest possible policy is the neutral policy that carries no information
and does nothing. Its set of policy states $\POLS$ is the unit type, and its
policy step function is the constant function that produces the unit, $\lambda
\_ . \top$, thereby allowing all calls the machine step function. This
corresponds to the lifting of our machine model to the policy setting.

\paragraph*{Software-only policies}
%
\rb{TODO In a way, in these schemes the policy state is built in as part of the
  program state and transparent to the hardware, although it could be simulated
  by an overlay where enforcement is represented at the policy level.}

\paragraph*{Capability machines}
%
\rb{TODO Here the policy is built into the hardware, although the extended ISA
  could be split into a machine without capabilities and capabilities as the
  policy.}

\newcommand{\TAGS}{\mathcal{T}}
\newcommand{\tagname}{t}
\newcommand{\uP}{{\mu P}}

\paragraph*{Micropolicies}
%
\rb{TODO Similarly to above, should we consider tags as part of the machine or part of the
  policy? }
